D3064R0: Bringing the Laws of Physics to Bear on the OOTA Problem

### 2024-01-11 ootavacuous.tex
Add a table of contents
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Add more elaborate non-trivial sdep example
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

>>>>

\tableofcontents

@@

Much more elaborate examples can be constructed, for example,
involving sums of products of values loaded.
Reverting back to short-form code fragments, consider the following:

\begin{quote}
	\co{z = w * x + w * y + w;}
\end{quote}

This has the following semantic dependencies when all of \co{w},
\co{x}, and \co{y} are zero:

\begin{enumerate}
\item	From the combination of \co{w} and \co{x} to \co{z}.
\item	From the combination of \co{w} and \co{y} to \co{z}.
\item	From \co{w} to \co{z}.
\end{enumerate}

Despite appearances, these are not redundant.
The last semantic dependency does not imply the first, because given
that \co{w} becomes non-zero, a change in \co{x} further changes
the value stored to \co{z}.
Similar reasoning shows that the last semantic dependency does not
imply the second.
Much more elaborate examples can easily be constructed.

This raises the question of how to determine the set of semantic
dependencies in a given execution of a given fragment of code.
The short answer is that when running on a real-world system, 
any C++ program is a finite-state machine, which, unlike Turing-complete
systems, can be analyzed.
% @@@ reference to cbmc appendix.
